Neural Network Language Models for Automatic Speech Recognition

### 2018-12-10 paper/paper.tex
paper: Add more detail on WikiText and Gigaword, including EDA images

@@

This dataset is based on articles from
Wikipedia, containing 2,088,628 tokens
in the training set, 245,569 tokens in
the test set and 217,646 tokens in the
validation set.

@@

This dataset contained quite a lot of
technical or domain specific
terminology due to the fact that the
sentences within were derived from
encyclopedic articles. This inherently
makes accurate prediction difficult, since
there is a higher likelihood that the
following word might be infrequent in the
corpus.

>>>>

\section{WikiText}
\label{sec:wikitext}

@@

This dataset is based on articles from Wikipedia, containing 1,756,924 tokens in
the training set, 184,354 tokens in the validation set and 207,080 tokens
in the test set. The combined dictionary for all three sets contains 28,755
unique tokens.

\begin{figure}[h]
\includegraphics{sr-eda-wikitext-train-words}
\includegraphics{sr-eda-wikitext-valid-words}
\centering
\caption{Training and Validation words in the WikiText dataset}
\end{figure}

Notice that because of the large amount of domain specific language that is used
due to the fact that the sentences within were derived from encyclopedic
articles, the dataset contains a large number of "unknown" tokens. An "unknown"
token, represents any token with a frequency below the dataset threshold. This
inherently makes accurate prediction difficult, since there is a higher
likelihood that the following word might be infrequent in the corpus.

@@

Also notice the most frequent bigrams and trigrams of the dataset

\begin{figure}[h]
\includegraphics{sr-eda-wikitext-bigrams}
\includegraphics{sr-eda-wikitext-trigrams}
\centering
\caption{Training set Bigrams and Trigrams in the WikiText dataset}
\end{figure}

The bigrams and trigrams in the dataset indicate that the dataset is, as expected,
most describing phenomena or objects, with large frequencies for bigrams
such as "in the" or "of the". The trigrams also reveal that domain specific
descriptions-in-general are frequently occurring, ("unk unk unk").

\section{Gigaword}
\label{sec:gigaword}

The second dataset we used was Gigaword. This dataset is based on ____,
containing 110,382,986 tokens in the training set, 549,0454 tokens in the
validation set and ____ tokens in the test set. The combined dictionary
contains ____ unique tokens.

____

\begin{figure}[h]
\includegraphics{sr-eda-gigaword-train-words}
\includegraphics{sr-eda-gigaword-valid-words}
\centering
\caption{Training and Validation words in the Gigaword dataset}
\end{figure}

In contrast to WikiText, there are a smaller number of domain-specific
words and instead more words similar to those typically used in news
articles, "said", "government", "stock", "tuesday", etc.

\begin{figure}[h]
\includegraphics{sr-eda-gigaword-bigrams}
\includegraphics{sr-eda-gigaword-trigrams}
\centering
\caption{Bigrams and Trigrams words in the Gigaword training set}
\end{figure}

Also notice that bigrams and trigrams for this dataset reveal that a
large number of articles are talking about the same thing, for instance
"the united states", "the european union" and "george w bush".
